How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-24 Manuscript.tex
Updates from ShareLaTeX

\title{How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{3} 
\author{
\alignauthor 
Rahul~Krishna\\Tim Menzies, Xipeng~Shen \\
       \affaddr{Com. Sci., NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Naveen   Lekkalapudi\\
 \affaddr{Bellhops } \\ 
       \affaddr{Washington D.C.}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of just predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  what to change  in order to
 improve on the predicted values.
This paper defines an evaluation strategy for evaluating such  planners and applies it to four different planning methods.
It is shown that our  strategy  can (a) recognize   inferior planning methods and  (b) select useful planning methods.
Using the best method found by this evaluation strategy,  we can
reduce
 the expected values of defect counts and  runtimes of software projects to    
 45\%,61.5\%  (median) and 22\%,6\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
Business users are demanding  tools that support    business-level interpretations of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in software analytics~\cite{menzies12a}. Panelists commented  ``prediction is all well and good, but what about decision making?''. Note that these panelists were more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. So:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
In response to this business-level demands for planners,
we propose a novel {\em planning} approach called XTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. This paper uses XTREES
to reduce  the expected value of:
\bi
\item  Defects     in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item Runtimes   in   software    configured by  Siegmund et al.~\cite{sven12}.
\ei 
The approach discussed here is novel since most data miners used in software analytics
comment on ``what is'' and not ``what to do''. For example, a clustering
algorithm might find clumps of similar examples, but does not comment on the minimal
change(s) required to move from clump to clump.

@@

\section{Preliminaries}\label{sect:prelim}
\subsection{From Prediction to Planning}

This paper is about the next step {\em after} prediction. Suppose
a business user is presented a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. This user may
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?''

@@

This pattern of \fig{howxy} (where the displaced test cases are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training data have some authority in the regions
used to generate the plans\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.

@@

	\begin{figure}[!t]
	\begin{shaded}
  ~\hrule~

 {\bf Figure 5.A: Measuring Variability}

@@

	{\bf Figure 5.B: Measuring distance}

@@

	{\bf Figure 5.C: Top-down Clustering with WHERE}

@@

	{\bf Figure 5.D: Top-down division with Decision Trees}

@@

	 ~\hrule~
	  \end{shaded}
		\caption{Some algorithms used in this paper.}\label{fig:where}
		\end{figure}

\section{Four Planning Methods}
In his textbook on empirical methods, Cohen~\cite{cohen95} advises that any supposedly better
algorithm should be baselined against simpler alternatives. Accordingly,
this section described XTREES (which we call Method4) against three  
alternatives: 
  \bi
  \item  
  Method1, Method2 and Method3 use the   top-down
	bi-clustering method described in \fig{where}.C  which recursively divides the
	data in two  using a dimension that captures the greatest variability in the data. 
	\item
 Method4 uses the decision tree learner of \fig{where}.D. 
  \ei
  Note that all our methods have the two properties proposed in \tion{prelim}:
  \bi
  \item They find different plans in different parts of the data;
  \item They  are {\em trust-increasing} in the manner described in \tion{trust};
  i.e. they change changing examples such that they move {\em closer} to the training data.
  \ei
The following descriptions of the methods adopts the following convention. All variables
  set via  our engineering judgement  with Greek letters; e.g. $\alpha,\beta,\gamma$.
  In this paper, we show our current settings to these variables produces useful
  results. Elsewhere\cite{krall14,fu:ase15}, we are exploring tuning methods to 
  find better settings but  we have nothing definitive yet to report
  on auto-tuning planners.

@@

\subsection{Method2 = \\\CD+FS =  Method1  + Feature Selection }

{\em Summary:} Method2 works like Method1, but this time, it only mentions the most
informative features. Hence, Method2's plans are simpler.

@@

Based on the above, it might be possible to simplify Method1's plans by pruning back the features used to make
the plans. Following on from Papakroni, our Method2 returns plans
containing just the top $\beta=33\%$ most informative features. Here, ``informative'' means
that the values of a feature are good for selecting a small set of clusters (ideally,
just one).
This can be estimated using the Fayyad-Iranni INFOGAIN algorithm~\cite{FayIra93Multi}
as follows.

Firstly, 
run  WHERE to generate   clusters/ Next,
discretize numeric features using the Fayyad-Iranni discretizer
(divide numeric columns into bins $B_i$, each of which  select for the fewest cluster ids).
Let feature $F$ have bins $B_i$, each of which contains $n_i$ rows
and 
let each bin $B_i$ have entropy $e_i$ computed from the frequency of clusters seen in that bin (computed from \fig{where}.A).
Cull the features as per Papakroni; i.e. just use the $\beta=33\%$ most informative features
where  the   value of  feature $F$ is $\sum_i e_i\frac{n_i}{N}$ ($N$ is the number of rows).

After that, Method2 works line Method1 but now the   plans  only
mention the $\beta=33\%$ most informative features.
\subsection{Method3 = BIC = Method2 + Best-in-cluster}\label{sect:BIC}

@@

{\em Details:}
One problem with Method2 is that it makes little use of the detailed knowledge
of the examples that are squashed together to form the centroids. Accordingly,
our Method3 works like Method2 but some important differences.

In Method3, clusters are summarized in {\em two} examples: (1)~the centroid found in Method1 and
(2)~the best-in-cluster example; i.e. the  example in that cluster
with the best performance score.
Next, as before, each centroid $C_i$ is annotated with the nearest centroid $C_j$
with a better performance score.
Howver, after that,  when generating a plan for a test instance, Method3:
\bi
\item
Find the test cases's nearest centroid $C_i$;
\item
Finds the associated better centroid $C_j$ and its associated best-in-cluster example.
\item
Computes a plan to change the test case  from the delta between the test case
and the best in that $C_j$ cluster.
\ei
Note that, as with Method2, this method's plans only mentions the  $\beta=33\%$ most informative features. 
%\input{tex/pseudo-code-1.tex}

@@

\subsection{Method4 = XTREES = Deltas in Decision Tree Branches}

@@

{\em Details:} One potential problem with Methods 1,2 and 3 is the {\em unsupervised} nature of
the algorithm used for the initial clustering. Unsupervised methods like WHERE
execute without knowledge of the target class.
{\em Supervised} methods, on the other hand, are allowed to reflect on more knowledge including
the values in the target class. In theory, this extra knowledge can lead to better data mining.
Accordingly, Method4 uses a supervised method to generate its plans.

In summary, XTREES uses the decision tree algorithm of \fig{where}.D to divide the data.
Decision trees have branches down to leaves. 
XTREES builds plans by asking three questions:
\be
\item
What {\em current} branch does a test case fall in?
\item What {\em desired} branch would the test case want to move to?
\item What are the {\em deltas} between current and desired? 
\ee
The last question can be answered by finding the deltas in branches of the decision tree that lead to {\em desired} from {\em current}. For full algorithmic details, refer to \fig{xtrees_bare}.

@@

\begin{figure}[!t]
\small 
\[
\begin{array}{r}
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; HOW)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{actual}& =\mathrm{Defects \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{actual} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} \mathit{actual},\mathit{after}
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]

@@

\subsection{Setup}

In the experiments shown below,  we use the planners to comment on how to reduce
software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be manually adjusted by programmers or (for large scale changes) automatically adjusted using code refactoring
tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}.

\fig{work} shows our proposal to verify if the recommendations made by our planners actually work. Accordingly, we divide the
project data  into two disjoint sets {\em train} and {\em test}
(so \mbox{{\em train} $\cap ${\em test} $=\;\emptyset$}).
Next, from the train set, we build both a {\em planner} as well
as a {\em  predictor}. Our general framework does not   commit to any particular choice of { planner} or { predictor} but, for the purposes of this paper, our {\em planner} will be from \ref{clust_contrast} and our {\em predictor} will be the Random Forest Classifier~\cite{Breiman2001} and Random Forest Regressor taken from the SciKit Learn toolkit~\cite{Pedregosa2012}.

As for the {\em test} data, this is passed to the { predictor}
to measure the baseline prediction accuracy, false alarm, and recall.
If our { predictors} fail to perform adequately on the test data,
then we cannot trust them to comment on our plans. Accordingly,
if that performance is unsatisfactory, we abort.
Else, we (1)~apply the { planner} to alter the {\em test} data;
then (2)~apply the { predictor} to the altered data $test'$;
then (3)~return data on the {\em before, after} predictions.

\subsection{Data}

@@

The clear advantage of our current work is that it can be readily and automatically applied to domains with historical data. However, the obvious drawback with this approach is that our assessment of the plans is only as good as the predictor. To mitigate for this {\em problem of poor predictors}, it is wise to demand certain standards for {\em satisfactory} thresholds.

\subsection{Assessment}
\fig{work} showed how we build and test our planners. The dependent variables of Jureczko and Siegmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Siegmund data. Additionally, for both the data sets, we designed a setup that repeated the trials 40 times (the value 40 was chosen to satisfy the minimum sample size requirements of the central limit theorem):
\bi
\item For Siegmund data, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data.
\item For the Jureczko data, we used the training and testing sets of \fig{j}. 
\ei
The 40 repeats defined above were repeated for each planner. A Scott-Knott procedure was used to test for statistical differences in the result. The Scott-Knott procedure was recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{mittas13}.

This method
sorts a list of $l$ treatments with $ls$ measurements by their median
score. It then
splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
 differences  in the observed performances
before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
 $E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2$.
Scott-Knott  applies an  hypothesis test $H$ to check
if $m,n$ are significantly different. If so, Scott-Knott  recurses on the splits.

The hypothesis test $H$ used here is a conjunction of the A12 effect size test and a non-parametric bootstrap sampling. In other words, the Scott-Knott procedure being used here divides the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$). For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if an hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

\subsection{Results}
\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}	whye where?
Recent results suggest that, when clustering on independent variables of software project data,
	we are free to select from a wide range of 
	clustering methods.  Ganesan~\cite{div14} explored 
	different clustering methods for SE data using   effort and defect data from
	the PROMISE repository~\cite{promiserepo}.
	That study explored
	K-Means, mini-batch-K-Means, DBscan, EM, Ward, and the WHERE algorithm discussed
	below.
	Clusters were assessed via the performance of prediction 
	learned from the clusters by Random Forests (for defect prediction)
	and M5prime or linear regression (for effect estimation).  Ganesan found
	that the details of the clustering method were less important than ensuring that  a large number of clusters were generated.
	Accordingly, for clustering, we select a clustering method that generates a large
	number of small cluster
	($\sqrt{N}$ clusters
	from $N$ examples) that runs fasts, which has shown promise in prior work~\cite{Menzies2013}, and which ignores spurious dimensions (the last item is important since, in our experience, much SE data is ``noisey''; i.e. contains signals not associated with the target variable.

\section{Threats to Validity}
\section{Related Work}
dashboards

@@

>>>>

\title{How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{3} 
\author{
\alignauthor 
Rahul~Krishna\\Tim Menzies, Xipeng~Shen \\
       \affaddr{Com. Sci., NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Naveen   Lekkalapudi\\
 \affaddr{Bellhops } \\ 
       \affaddr{Washington D.C.}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of just predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  what to change  in order to
 improve on the predicted values.

This presents such a tool, called XTREES and evaluates it against three alternatives.
In our experiments, XTREES reduced
 the expected values of defect counts and  runtimes of software projects to    
 45\%,61.5\%  (median) and 22\%,6\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
Business users are demanding  tools that support    business-level interpretations of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in software analytics~\cite{menzies12a}. Panelists commented  ``prediction is all well and good, but what about decision making?''. Note that these panelists were more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. So:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
In response to this business-level demands for planners,
we propose a novel {\em planning} approach called XTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. This paper uses XTREES
to reduce  the expected value of:
\bi
\item  Defects     in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item Runtimes   in   software    configured by  Siegmund et al.~\cite{sven12}.
\ei 
The approach discussed here is novel since most data miners used in software analytics
comment on ``what is'' and not ``what to do''. For example, a clustering
algorithm might find clumps of similar examples, but does not comment on the minimal
change(s) required to move from clump to clump.

@@

\section{Preliminaries}\label{sect:prelim}

\subsection{From Prediction to Planning}

This paper is about the next step {\em after} prediction. Suppose
a business user is presented a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. This user may
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?''.

@@

This pattern of \fig{howxy} (where the changes examples are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training data have some authority in the regions
used to generate the plans\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.

@@

	\begin{figure} 
	\begin{shaded}
  ~\hrule~

 {\bf Figure 7.A: Measuring Variability}

@@

	{\bf Figure 7.B: Measuring distance}

@@

	{\bf Figure 7.C: Top-down Clustering with WHERE}

@@

	{\bf Figure 7.D: Top-down division with Decision Trees}

@@

	 	{\bf Figure 7.E: Finding the most informative rows}

Discretize all numeric features using the Fayyad-Iranni discretizer~\cite{FayIra93Multi}
(divide numeric columns into bins $B_i$, each of which  select for the fewest cluster ids).
Let feature $F$ have bins $B_i$, each of which contains $n_i$ rows
and 
let each bin $B_i$ have entropy $e_i$ computed from the frequency of clusters seen in that bin (computed from \fig{where}.A).
Cull the the features as per Papakroni~\cite{papa13}; i.e. just use the $\beta=33\%$ most informative features
where  the   value of  feature $F$ is $\sum_i e_i\frac{n_i}{N}$ ($N$ is the number of rows).

	  \end{shaded}
		\caption{Some algorithms used in this paper.}\label{fig:where}
		\end{figure}

\section{Four Planning Methods}
In his textbook on empirical methods, Cohen~\cite{cohen95} advises that any supposedly better
algorithm should be baselined against simpler alternatives. Accordingly,
this section described XTREES (which we call Method4) against three  
alternatives: 
  \bi
  \item  
  Method1, Method2 and Method3 use the   top-down
	bi-clustering method described in \fig{where}.C  which recursively divides the
	data in two  using a dimension that captures the greatest variability in the data. 
	\item
 Method4 uses the decision tree learner of \fig{where}.D. 
  \ei
  Note that all our methods have the two properties proposed in \tion{prelim}:
  \bi
  \item They are {\em local learners}; i.e. different test examples
  will be given plans that are specialized  to their particulars;
  \item They  are {\em trust-increasing} in the manner described in \tion{trust};
  i.e. they change changing examples such that they move {\em closer} to the training data.
  \ei
The following descriptions of the methods adopts the following convention. All variables
  set via  our engineering judgement  with Greek letters; e.g. $\alpha,\beta,\gamma$.
  In this paper, we show our current settings to these variables produces useful
  results. Elsewhere\cite{krall14,fu:ase15}, we are exploring tuning methods to 
  find better settings but  we have nothing definitive yet to report
  on auto-tuning planners.

@@

\subsection{Method2 =  CD+FS = \\ Method1  + Feature Selection }

{\em Summary:} Method2 works line Method1 but now the   plans  only
mention the $\beta=33\%$ most informative features. Hence, Method2's plans are simpler.

@@

Based on the above, it might be possible to simplify Method1's plans by pruning back the features used to make
the plans. Following on from Papakroni, our Method2 returns plans
containing just the top $\beta=33\%$ most informative features. Here, ``informative'' means
that the values of a feature are good for selecting a small set of clusters (ideally,
just one).
This can be estimated using the Fayyad-Iranni INFOGAIN algorithm~\cite{FayIra93Multi}
of \fig{where}.E.

\subsection{Method3 = BIC = \\  Method2 + Best-in-cluster}\label{sect:BIC}

@@

{\em Details:}
One problem with Method2 is that it makes little use of the detailed knowledge
of the examples that were squashed together to form the centroids. 
Hence,
in Method3, we collect more information about each cluster.

Method3 summarizes clusters into {\em two} examples: (1)~the centroid $C_x$ found in Method1 and
(2)~the best-in-cluster $B_x$  example; i.e. the  example in that cluster
with the best performance score. 
For the Siegmud data, $B_x$ is the cluster member with the fastest runtime;
for the Jureczko data, $B_x$  is the cluster member with lowest raw defect count
(resolving ties at random).

Next,  each centroid is connected by a line to its nearest centroid.
 In that line, we say $C_i,C_j$ are the centroids associated with worst/best centroid performance scores.

For each test instance, Method3 
find the nearest line; selects the  best end $C_j$ of that line;  then extracts $B_j$ (which is the
 best-in-cluster associated with  $C_j$).
The returned plan is then computed   from the delta between the test case
and $B_j$.
Note that, as with Method2, this method's plans only mentions the  $\beta=33\%$ most informative features. 
%\input{tex/pseudo-code-1.tex}

@@

\subsection{Method4 =  XTREES =\\ Deltas in Decision Tree Branches}

@@

{\em Details:} One potential problem with Methods 1,2 and 3 is the {\em unsupervised} nature of
the algorithm used for the initial clustering. Unsupervised methods like WHERE
execute without knowledge of the target class.
{\em Supervised} methods, on the other hand, are allowed to reflect on more knowledge including
the values in the target class. In theory, this extra knowledge can lead to better data mining.
Accordingly, XTREES uses a supervised method to generate its plans.
Specifically, it  uses the decision tree algorithm of \fig{where}.D to divide the data.
Next, XTREES builds plans from the branches of the decision trees. It does so by asking three questions:
\be
\item
What {\em current} branch does a test case fall in?
\item What {\em desired} branch would the test case want to move to?
\item What are the {\em deltas} between current and desired? 
\ee
The last question can be answered by finding the deltas in branches of the decision tree that lead to {\em desired} from {\em current}. For full algorithmic details, refer to \fig{xtrees_bare}.

@@

\begin{figure}[!b]
\small 
\[
\begin{array}{r}
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; XTREES)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{before}& =\mathrm{Performance\; scores \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{before} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} R=\frac{\mathit{after}}{\mathit{before}}
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]

@@

This section describes an experimental design (and results) for evaluating the above four methods.

\subsection{A Strategy for Evaluation Planners}

\subsubsection{Performance Measures}

For a planning system designed for business users, we seek two properties:
\bi
\item {\em Effectiveness:}    i.e.  if  its recommendations  are  applied  then  some  statistically significant  change  should  be  observed. 
\item {\em Succinctness:} given two plans with the same effectiveness, we prefer the shorter one.
Such shorter plans are easier to explain (less to show) and faster to implement (less to change).
\ei
 In the following, we will show that XTREES and one other method (BIC) are equally effective
 but XTREES is more succinct (proposes changes to fewer features).

\subsubsection{Collecting Data}

\fig{work} shows our experimental design.  Initially, we divide the
project data  into two disjoint sets {\em train} and {\em test}
(so \mbox{{\em train} $\cap ${\em test} $=\;\emptyset$}).
Next, from the train set, we build both a {\em planner} and
 a {\em  predictor}.

Our general framework does not   commit to any particular choice of { planner} or { predictor} but, for the purposes of this paper:
\bi
\item Our {\em planner} will be one of Methods 1,2,3,4;
\item Our  {\em predictor} will be the Random Forest Classifier~\cite{Breiman2001} (for discrete classes) and Random Forest Regressor (for continuous classes) taken from  SciKit Learn~\cite{Pedregosa2012}.   We use these
data miners since extensive studies have shown these to be amongst the better alternatives for mining software data~\cite{lessmann}.
\ei
As for the {\em test} data, this is passed to the { predictor}
to measure performance statistics related to effectiveness.

If our { predictors} fail to perform effectively on the test data,
then we cannot trust them to comment on our plans. Accordingly,
if that performance is unsatisfactory, we abort. Recall from the above discussion that this step indicated
we should not use some of the  Jureczko data.

Else, we (1)~apply the { planner} to alter the {\em test} data;
then (2)~apply the { predictor} to the altered data $test'$;
then (3)~return data on the {\em before, after} predictions expressed as the ratio $R=\frac{\mathit{after}}{\mathit{before}}$.
This is a unit-less ratio with the following properties:
\bi
\item If $R= 1$, this means  ``no change from baseline''; 
\item If $R < 1$, this indicates some reduction to the baseline;
\item If $R > 1$, this indicates ``optimization failure''.
\ei
Also, to measure succinctness, we count the number of features in the plan.

\subsubsection{Studying Repeated Samples}
Our methods contain some stochastic algorithms; e.g. WHERE's selection of ``what example to explore first'' (see \fig{where}.C) and
  XTREES' occasional use of a random guess when deciding what part of a discretized range to include in the plan
  (see \fig{xtrees_bare}). Hence, we report the $R$ values seen in 40 repeated runs
  (with different random number seeds).
The the value 40 was chosen to be  larger than the 30 samples  required
to satisfy the central limit theorem.

Our results are presented by the line diagrams like those shown on the right-hand-side of the following example table.
The black dot shows the median $R$ value and the horizontal likes stretch over the inter-quartile
range (hereafter, IQR) that is the space from the 25th percentile value to
the 75th percentile value.

\begin{center}

{\small  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~}c@{}r}}\hline
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
1 &         XTREE &    0.49  &  0.13 & \quart{7}{25}{17}{115} \\\hline  
2 &      CD &    0.59  &  0.18 & \quart{15}{34}{36}{115} \\
2 &          BIC &    0.60  &  0.12 & \quart{24}{24}{38}{115} \\\hline  
3 &      CD+FS &    0.62  &  0.06 & \quart{36}{12}{42}{115} \arrayrulecolor{black}\\\hline \end{tabular}}
\end{center}

In this example, the rows are  sorted on the median values of each method. Note that all the methods
have   $R<1$ values; i.e. all these methods reduced the expected value of the performance score in that experiment
while XTREE achieved the greatest reduction (down to 49\% of the original value).

The above table has a  left-hand-side  {\bf Rank} column. This column reports if
the values for each method are statistically different and are more than trivially different. 
In this example, table, CD and BIC are ranked together while XTREES and CD+FS are ranked best and worst, respectively.

  \subsubsection{Statistical Methods}
  We compute {\bf Rank} using a Scott-Knott test recommended by Mittas and  Angelis~\cite{mittas13}. 
In that test, using the median values of each method,  
sort a list of  $l=40$ values of $R$ values found in  $ls=4$ different methods. 
Then,
splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
 differences  in the observed performances
before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
 \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
Scott-Knott  applies an statistical  hypothesis test $H$ to check
if $m,n$ are significantly different  (in our case, the conjunction of A12 and bootstrapping). 
If so, Scott-Knott  recurses on the splits.
In other words, the Scott-Knott procedure being used here divides the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$).

For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if an hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

@@

\subsection{Results}

all the smoting and tuning running in train.

  The dependent variables of Jureczko and Siegmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Siegmund data.
\bi
\item For Siegmund data, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data.
\item For the Jureczko data, we used the training and testing sets of \fig{j}. 
\ei
The 40 repeats defined above were repeated for each planner and the results processed as described in the last section.

\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}

\section{Related work}
results suggest that, when clustering on independent variables of software project data,
	we are free to select from a wide range of 
	clustering methods.  Ganesan~\cite{div14} explored 
	different clustering methods for SE data using   effort and defect data from
	the PROMISE repository~\cite{promiserepo}.
	That study explored
	K-Means, mini-batch-K-Means, DBscan, EM, Ward, and the WHERE algorithm discussed
	below.
	Clusters were assessed via the performance of prediction 
	learned from the clusters by Random Forests (for defect prediction)
	and M5prime or linear regression (for effect estimation).  Ganesan found
	that the details of the clustering method were less important than ensuring that  a large number of clusters were generated.
	Accordingly, for clustering, we select a clustering method that generates a large
	number of small cluster
	($\sqrt{N}$ clusters
	from $N$ examples) that runs fasts, which has shown promise in prior work~\cite{Menzies2013}, and which ignores spurious dimensions (the last item is important since, in our experience, much SE data is ``noisey''; i.e. contains signals not associated with the target variable.
	ats to Validity}

\section{Related Work}
dashboards

@@

Many data mining methods offer a succinct summary of project data
e.g. see the Bayes nets
favored by Dejaeger et al.~\cite{Dejaeger13}; or   the regression models
learned by Nagappan~\cite{Nagappan05}.
Another  technique is to offer a dashboard that visualizes project data.
For example, the dashboards
provided by the Hackystat team~\cite{Johnson09} presents extensive and detailed
summaries of programmer behavior.

Some users do not like being told what to do... they prefer to have the current world explained to them 
-- but those dashboards typically do not learn threshold points
(that report where action is needed) nor do they offer specific advice on what actions to take.
